---
title: "Universities & Colleges with Actuarial Programs (UCAP):"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

# Introduction:

In this project, web scraping was used to gather information about universities around the world that offer bachelor's, master's, and PhD programs in actuarial science. The data was collected from the Society of Actuaries' Listing of Universities and Colleges with Actuarial Programs, but it should be noted that this project does not guarantee the accuracy of the information. If you need a reliable list of institutions, please visit the SOA's website at [**https://www.soa.org/institutions/**](https://www.soa.org/institutions/).

This project was completed as part of my research on master's degree programs in actuarial science in the United States and has been recognized by the SOA.

## Library Used

Following are the list of package used for the purpose of this project.

-   `dplyr` : For data manipulation

-   `rvest` : For web scraping

-   `tidyr` : For Data cleaning

-   `stringr` : for manipulating string

-   `janitor` : cleaning names

-   `ggplo2` : for creating graphs

-   `gt` : for creating tables

### Loading library

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(dplyr)
library(tidyr)
library(rvest)
library(janitor)
library(stringr)
library(gt)
library(ggplot2)
```

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
pretty_table<- function(df,title)
  {
as_raw_html(
  df %>% 
    gt() %>%
    tab_header(title = title) %>%
    tab_source_note(source_note =  md("*Data from SOA website*")) %>%
    tab_options(
        table.border.top.color = "white",
        heading.border.bottom.color = "black",
        row_group.border.top.color = "black",
        row_group.border.bottom.color = "white",
        stub.border.color = "transparent",
        table.border.bottom.color = "white",
        column_labels.border.top.color = "black",
        column_labels.border.bottom.color = "black",
        table_body.border.bottom.color = "black",
        table_body.hlines.color = "white"
    ))
    
}
```

## Web scraping

To extract table from webpage using `R`, we need `rvest` package.

First we need to install and lead the `rvest` package which i have already done in previous section

Next, use the `read_html()` function to read the HTML content of the webpage into R.

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
url <- "https://www.soa.org/institutions/"
html <- read_html(url)
```

After this , Use the `html_nodes()` function to find the table element in the HTML.We can use `css` argument to specify a CSS selector that matches the table elements

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
table <- html_nodes(html, css = "table")

```

At last , we use `html_table()` function to extract the table data from the table element. This returns a list of data frames, one for each table on the webpage. Since there is only one table, i have used `[[1]]` to extract the first element of the list which is the data frame for the table that we required

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
df <- html_table(table)[[1]]
```

## Data Cleaning

In r programming , we need to perform series of steps to fix or remove any issues with the data such as errors, missing values or inconsistencies.

Here are the problem that i obeserved and perform to clean a data frame:

### Standardize variable names and values

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
df <- df %>%
  janitor::clean_names()
#pretty_table(df=head(df),title = "Sample 5")
```

### Inconsistencies

```{r}
df <- df %>%
  separate_rows(level_of_actuarial_courses_offered, sep = ",")
#pretty_table(df = head(df),title = "Sample 5")
```

### Unnecessary white space

```{r}
df <- df %>%
  mutate(country_territory = str_trim(country_territory),
         level_of_actuarial_courses_offered = str_trim(level_of_actuarial_courses_offered))
#pretty_table(df=head(df),title = "Sample 5")

```

## Data Exploration

The purpose of this project is to find list of US Universities offering Masters program in actuarial science and are in list of recognized university of SOA

for this we need to perform the following task in R:

```{r}
df1 <- df %>%
  filter(level_of_actuarial_courses_offered == "Masters" & country_territory =="United States")

pretty_table(head(df),"sample 5")
```

### Getting US University list based on SOA recognition tier

The UCAP list includes universities and colleges that have met certain eligibility requirements for recognition as Centers of Actuarial Excellence (CAEs), or as having Introductory Curriculum (UCAP-IC) or Advanced Curriculum (UCAP-AC) status. To be recognized as a CAE, a university must meet eight specific requirements related to its degree programs, curriculum, faculty composition, graduate quality, and other factors. Universities with UCAP-IC status must offer course coverage for at least two SOA preliminary exams and have approved courses for at least one Validation by Educational Experience (VEE) topic area. Universities with UCAP-AC status must offer course coverage for at least four SOA preliminary exams, including Exam LTAM or Exam STAM, and approved courses for all VEE topic areas. The UCAP program also includes a University-Earned Credit (UEC) program, which allows university students to become eligible for SOA exam credit by attaining a designated UEC mark on university courses at approved CAEs.

So lets get list for each tier

-   `CAE with UEC` : University-Earned Credit Status:

    ```{r}
    uec <- df1 %>%
      filter(soa_recognition_tier == "CAE/UEC")
    pretty_table(df=uec,title = "List of University in CAE with UEC tier")

    ```

-   `CAE` : Centers of Actuarial Excellence

    ```{r}
    cae<- df1 %>%
      filter(soa_recognition_tier == "CAE")

    pretty_table(df=cae,title = "List of University in CAE tier")
    ```

-   `UCAP-AC`: Advanced Curriculum

    ```{r}
    ac <- df1 %>%
      filter(soa_recognition_tier == "UCAP-AC")

    pretty_table(df=ac,title = "List of University in AC tier")
    ```

-   `UCAP-IC` : Introductory Curriculum

    ```{r}
    ic <- df1 %>%
      filter(soa_recognition_tier == "UCAP-IC")

    pretty_table(df=ic,title = "List of University in IC tier")
    ```

### 

### Other then US university

Now lets look at university other than in USA .

First lets try finding country having more number of university who falls in the `SOA` tier

```{r}
df2 <- df %>%
  filter(level_of_actuarial_courses_offered == "Masters" & country_territory !="United States") %>%
  group_by(country_territory) %>%
  summarise(number=n()) %>%
  filter(number>1) %>%
  ungroup()

plot1<- ggplot(data = df2,aes(x=reorder(country_territory,number),y=number,fill=country_territory))+
  geom_col()+
  scale_fill_brewer(palette = "Set1")+
  geom_text(aes(label = number), vjust = -0.2, size = 5) +
  labs(
    title ="Country other then USA",
    subtitle="Listed in SOA(for Masters)",
    x="Country",
    y="No of Programs Offered"
  )
  
plot1 + theme(panel.background = element_rect(fill = "white", colour = "grey50"),
              legend.title= element_text(colour = "blue",size = 10,face="bold"),
              legend.background = element_rect(fill="lightblue",linewidth = 0.05,linetype = "solid"),
              legend.position = c(0.1,0.7))+
  guides(fill=guide_legend(title="country"))


```
