---
title: "Universities & Colleges with Actuarial Programs (UCAP):"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

# Introduction:

In this project, web scraping was used to gather information about universities around the world that offer bachelor's, master's, and PhD programs in actuarial science. The data was collected from the Society of Actuaries' Listing of Universities and Colleges with Actuarial Programs, but it should be noted that this project does not guarantee the accuracy of the information. If you need a reliable list of institutions, please visit the SOA's website at [**https://www.soa.org/institutions/**](https://www.soa.org/institutions/).

This project was completed as part of my research on master's degree programs in actuarial science in the United States and has been recognized by the SOA.

## Library Used

Following are the list of package used for the purpose of this project.

-   `dplyr` : For data manipulation

-   `rvest` : For web scraping

-   `tidyr` : For Data cleaning

-   `stringr` : for manipulating string

-   `janitor` : cleaning names

### Loading library

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(dplyr)
library(tidyr)
library(rvest)
library(janitor)
library(stringr)
```

## Web scraping

To extract table from webpage using `R`, we need `rvest` package.

First we need to install and lead the `rvest` package which i have already done in previous section

Next, use the `read_html()` function to read the HTML content of the webpage into R.

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
url <- "https://www.soa.org/institutions/"
html <- read_html(url)
```

After this , Use the `html_nodes()` function to find the table element in the HTML.We can use `css` argument to specify a CSS selector that matches the table elements

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
table <- html_nodes(html, css = "table")

```

At last , we use `html_table()` function to extract the table data from the table element. This returns a list of data frames, one for each table on the webpage. Since there is only one table, i have used `[[1]]` to extract the first element of the list which is the data frame for the table that we required

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
df <- html_table(table)[[1]]
```

## Data Cleaning

In r programming , we need to perform series of steps to fix or remove any issues with the data such as errors, missing values or inconsistencies.

Here are the problem that i obeserved and perform to clean a data frame:

### Standardize variable names and values

```{r}
df <- df %>%
  janitor::clean_names()
head(df)
```

### Inconsistencies 

```{r}
df <- df %>%
  separate_rows(level_of_actuarial_courses_offered, sep = ",")

head(df)
```

### Unnecessary white space

```{r}
df <- df %>%
  mutate(country_territory = str_trim(country_territory),
         level_of_actuarial_courses_offered = str_trim(level_of_actuarial_courses_offered))
head(df)
```
